Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2017-10-16 TACAS2018/paper.tex
sec 3.1 and 3.2 editing

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Model Semantics}\label{sec:model_semantics}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

\todo{This section should be integrated later, closer to the use of AA}

@@

Furthermore, a control system may have a derived
output that is a linear combination of its states and inputs, which may
restricts the observability of the statespace from the output space.
\begin{equation}
\label{eq:ode2}  
\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)
\end{equation}

@@

%where $\vec{w}$  is a continuous zero-mean white noise source with
%covariance $N ( 0 , Q )$ 
Furthermore, a control system may have a derived
output that is a linear combination of its states and inputs, which may
restricts the observability of the statespace from the output space.
\begin{equation}
\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)
\end{equation}

>>>>

Furthermore, a control system may have a derived
output that is a linear combination of its states and inputs, which may
restrict the observability of the statespace from the output space.
\begin{equation}
\label{eq:ode2}  
\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)
\end{equation}

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Model semantics of LTI models}\label{sec:model_semantics}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

@@

%where $\vec{w}$  is a continuous zero-mean white noise source with
%covariance $N ( 0 , Q )$ 
Furthermore, a control system may have a derived
output that is a linear combination of its states and inputs, which may
restrict the observability of the state-space from the output space.
\begin{equation}
\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)
\end{equation}
